---
title: "Covid Data"
format: html
editor: visual
---

::: callout-warning
## Data Manipulation Disclaimer

The data presented here has been intentionally manipulated for exploratory and teaching purposes. It should not be considered accurate or used for any practical applications. Please exercise caution and use it solely for educational or experimental purposes.
:::

**Source:** https://github.com/CSSEGISandData/COVID-19

**About:** COVID data curated by the Johns Hopkins University Center for Systems Science and Engineering. Raw data is analyzed to show number of new COVID cases per day in the USA by state. On March 10, 2023, the Johns Hopkins Coronavirus Resource Center ceased its collecting and reporting of global COVID-19 data.

## Clean up

```{r}
#| echo: true
#| output: false

library(tidyverse)
library(janitor)

# Read in raw data
covid_cases <- read_csv("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_US.csv", show_col_types = FALSE) |> 
  
  # Pivot data
  pivot_longer(cols = matches("^\\d"), names_to = "Date", values_to = "Cases") |> 
  
  # Select columns of interest
  select(Province_State, Date, Cases) |> 
  mutate(Date = mdy(Date)) |> 
  
  # Calculate number of new cases per day
  group_by(Province_State, Date) |> 
  summarise(State_Count = sum(Cases)) |>
  mutate(New_Cases = State_Count - lag(State_Count)) |>
  
  # Remove negative new_cases (likely reporting correction)
  filter(New_Cases >= 0) |> 
  
  # Clean Names
  clean_names()

# Save data
write_csv(covid_cases, "covid.csv")
```

## Final Data

### Dimensions

`r ncol(covid_cases)` Columns

`r nrow(covid_cases)` Rows

### Column Information

`province_state`: State or province in the United States of America.

`date`: Date of reporting.

`state_count`: Total number of confirmed COVID cases in state as of `Date`.

`new_cases`: Number of new confirmed COVID cases on `Date`.

## Preview

```{r}
#| echo: false

library(reactable)

reactable(covid_cases)
```
