---
title: "Stocks"
format: html
editor: visual
---

::: callout-warning
## Data Manipulation Disclaimer

The data presented here has been intentionally manipulated for exploratory and teaching purposes. It should not be considered accurate or used for any practical applications. Please exercise caution and use it solely for educational or experimental purposes.
:::

**Source:** https://www.kaggle.com/datasets/aayushmishra1512/faang-complete-stock-data/data

**About:** FAANG is a acronym for **F**acebook (Meta), **A**pple, **A**mazon, **N**etflix, and **G**oogle. This dataset contains historical stock data for FAANG companies.

## Clean up

```{r}
#| echo: true
#| output: false

library(tidyverse)
library(janitor)

# Read in Function
read_stock <- function(csv, company_name) {
  read_csv(csv, show_col_types = FALSE, na = "null") |> 
    mutate(company = company_name) |> 
    clean_names() |> 
    select(company, date, open, high, low, close, volume) |> 
    drop_na()
}
  
# Read in Stock Files
facebook <- read_stock("Facebook.csv", "Facebook")
apple <- read_stock("Apple.csv", "Apple")
amazon <- read_stock("Amazon.csv", "Amazon")
netflix <- read_stock("Netflix.csv", "Netflix")
google <- read_stock("Google.csv", "Google")

# Merge Into one Dataframe
stock_data <- bind_rows(facebook, apple, amazon, netflix, google)

# Save as CSV
write_csv(stock_data, "stocks.csv")
```

## Final Data

### Dimensions

`r ncol(stock_data)` Columns

`r nrow(stock_data)` Rows

### Column Information

`company`: Name of company.

`date`: Date.

`open`: Opening price of the stock.

`high`: Maximum price of stock.

`low`: Minimum price of stock.

`close`: Closing price of stock.

`volume`: Number of shares traded of that stock for the day.

## Preview

```{r}
#| echo: false

library(reactable)

reactable(stock_data)
```
